\problemname{Rhyming Words}

You are given a long row of $n$ letters, for simplicity chosen from \texttt{A}--\texttt{Z}. By starting and stopping reading the row at arbitrary positions, you can extract words, $\frac{n(n+1)}{2}$ in total. We do not restrict ourselves to actual Swedish words but accept any substring of the given row as a word. However, we are only interested in words with a specific number, $v$, of vowels. The vowels are $A, E, I, O, U, Y$.

Your task is to find the largest group of such words that all rhyme with each other. To avoid misunderstandings, we give a simple definition of rhyme that hopefully roughly matches your way of writing verse. Two words rhyme if they satisfy the following three conditions:

\begin{itemize}
	\item Both words must contain at least one vowel.
	\item From the first vowel in each word to the end, the words must be identical. That is, the words may only differ before their first vowel.
	\item The words must not be completely identical.
\end{itemize}

For example, \texttt{SJUNGA} and \texttt{UNGA} rhyme, \texttt{VARG} and \texttt{KARG} rhyme, but \texttt{VEDSTAPEL} and \texttt{KONSTAPEL} do not, nor do \texttt{DRYG} and \texttt{ODRYG}, or \texttt{TA} and \texttt{TA}.

Note that if $word_1$ rhymes with $word_2$ and $word_2$ rhymes with $word_3$, then $word_1$ automatically rhymes with $word_3$.

\section*{Input}
The first line contains an integer $1 \le n \le 10\,000$ indicating how many letters the long row of letters contains. The second line contains an integer $v$, $1 \le v \le 10$, indicating how many vowels the formed words should contain. The third and last line contains an unbroken sequence of $n$ letters $A...Z$. The number of vowels among them is always greater than $v$.

\section*{Output}
A single integer indicating the maximum number of words that
\begin{itemize}
	\item can be formed from the letter sequence by starting and stopping reading it at arbitrary positions, and
	\item contain exactly $v$ vowels, and
	\item rhyme with each other.
\end{itemize}
The words may overlap in the original sequence and they may start or end at the same position in the original sequence, but note that the same word may not be counted multiple times.
